Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
interesting -> of interest.
making ack one paragraph.
Remove leftover

    \begin{itemize}
        \item test discovery is not an aspect of BDD, only an emphasis
            on automating things is an aspect of BDD, so that
            \emph{testing is more fun} and \emph{things e.g. work with
            CI}.  This are two things, but both justify automation.
            We only need this to justify our discussion of Cabal
            integration and automatic test discovery.  If we remove
            those, we do not state that ``automation is an important
            aspect of BDD''.  This may be a solution.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but that we do not cover them.  This
            is very important.  And I think meaning got lost with the
            change, hence the revert.
    \end{itemize}

BDD includes TDD, but with a terminology and mindset shifted towards
specification instead of testing. In BDD, specifications can be used
for automatic testing.  BDD also includes other software development
methods, such as automatic test discovery and continuous
integration~\cite{ci}.  BDD-style TDD has been pioneered by
RSpec~\cite{rspec}.  In this paper, we explore how to apply the TDD
aspect of BDD to Haskell.

\end{quote}

@@

Hspec is thus useful for \emph{code documentation} but we observed that parts
of a specification can be useful as user documentation. To that end, we think
Python's {\tt doctest} module~\cite{doctest} is interesting.
It is not commonly described as a BDD tool, but we think it can be
used for BDD.
There is a Haskell version called Doctest\footnote{%
http://hackage.haskell.org/package/doctest}, which is integrated with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} from Haddock comments and
verifies them automatically.

@@

We are grateful to David Waern, Haddock's maintainer for reviewing and
accepting our patches to Haddock.

We would like to thank
Nick Smallbone for having improved QuickCheck so that
non-quantified properties are tested just once.

>>>>

    \begin{itemize}
        \item test discovery is not an aspect of BDD, only an emphasis
            on automating things is an aspect of BDD, so that
            \emph{testing is more fun} and \emph{things e.g. work with
            CI}.  This are two things, but both justify automation.
            We only need this to justify our discussion of Cabal
            integration and automatic test discovery.  If we remove
            those, we do not state that ``automation is an important
            aspect of BDD''.  This may be a solution.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but that we do not cover them.  This
            is very important.  And I think meaning got lost with the
            change, hence the revert.
    \end{itemize}
\end{quote}

@@

Hspec is thus useful for \emph{code documentation} but we observed that parts
of a specification can be useful as user documentation. To that end, 
Python's {\tt doctest} module~\cite{doctest} is of interest for us.
It is not commonly described as a BDD tool, but we think it can be
used for BDD.
There is a Haskell version called Doctest\footnote{%
http://hackage.haskell.org/package/doctest}, which is integrated with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} from Haddock comments and
verifies them automatically.

@@

We are grateful to David Waern, Haddock's maintainer for reviewing and
accepting our patches to Haddock.
We would like to thank
Nick Smallbone for having improved QuickCheck so that
non-quantified properties are tested just once.
